---
title: "Is this tweet from Trump or his staff?"
author: "Ying Yang"
date: "November 1, 2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What does this app do

This app is to predict whether a specific tweet is from Trump or Trump's staff.
You can type a tweet, the app will provide you the chance of this specific tweet that comes from Trump.

To run this applicaiton, you need to install a few packages in your R studio, including dplyr, purrr, tidyr, h2o, stringr, tidytext. It takes a little while to fit the model when start the app. Therefore, wait until the an image appears in the app before you type a new tweet.

Now, type a new tweet, click the button, you can see the probability of this tweet comes from Trump.



            
## Data

This is based on David Robinson's popular [sentiment analysis of Trumps tweets](http://varianceexplained.org/r/trump-tweets/). 
The data is provided by him from this [link]("http://varianceexplained.org/files/trump_tweets_df.rda"). 

There are 1512 tweets in this analysis.



## Slide with selected R code chunk
```{r, echo = TRUE, eval=FALSE}
        library(dplyr); library(purrr);library(tidyr); library(h2o)
        h2o.init()
        # load the data
        load(url("http://varianceexplained.org/files/trump_tweets_df.rda"))
        tweets <- trump_tweets_df %>%
                select(id, statusSource, text, created) %>%
                extract(statusSource, "source", "Twitter for (.*?)<") %>%
                filter(source %in% c("iPhone", "Android"))

        # Use the tidytext package to clean up the text a bit, remove stopwords
        reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"
        tweet_words <- tweets %>%
                        filter(!str_detect(text, '^"')) %>%
                        mutate(text = str_replace_all(text, 
                                                      "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
                        unnest_tokens(word, text, token = "regex", pattern = reg) %>%
                        filter(!(word %in% stop_words$word),
                               str_detect(word, "[a-z]"))
```

## Slide with Plot
Plot a wordcloud graph. Now you can go to the [App](https://yangyingtina.shinyapps.io/Shinny_App/)


```{r, echo = FALSE, message=FALSE}
setwd("C:/Users/User/Dropbox/Data Science/Jonhs Hopkins Courses/R coding practice _Ying/9. Developing Data Products/Final project")
load("DocumentTermMatrix_tweet.RData")
# word cloud
library(wordcloud, quietly = TRUE); library(dplyr)
tweet_words %>%
        count(word) %>%
        with(wordcloud(word, n, max.words = 100, color = "gray"))
```
 
Enjoy the App!
